Analysis for Biracial Grade Retention Project

### 2021-11-24 analysis/analysis.Rmd
Add lightbox support to analysis.Rmd output

---
title: "Analysis for Biracial Grade Retention Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

## Average adjusted preditions for biracials

>>>>

---
title: "Analysis for Biracial Grade Retention Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
    code_folding: hide
    lightbox: TRUE
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","acs.RData"))
```

@@

## Average adjusted predictions for biracials
